% !TEX encoding = UTF-8 Unicode

\begin{thebibliography}{x}
\addcontentsline{toc}{chapter}{\bibname}

\bibitem{rustbook}
Klabnik, Steve, and Carol Nichols. \emph{The Rust Programming Language}. \\
No Starch Press, 2018.

\bibitem{docrustlang}
Rust Documentation, hivatalos weboldal, \texttt{https://doc.rust-lang.org}, \\
Internet, 2019.

\bibitem{swift}
The Swift Programming Language, The Basics, \\
\texttt{https://docs.swift.org/swift-book/LanguageGuide/TheBasics.html}, \\
Internet, 2019. március.

\bibitem{tiobeindex}
TIOBE Index, hivatalos weboldal, \texttt{https://www.tiobe.com/tiobe-index}, \\
Internet, 2019. március.

\bibitem{servo}
Servo, the Parallel Browser Engine Project, \texttt{https://servo.org/}, Internet, 2019. március.

\bibitem{redox}
Redox OS, hivatalos weboldal, \texttt{https://www.redox-os.org/}, Internet, 2019. március.

\bibitem{haskellorg}
Haskell, hivatalos weboldal, \texttt{https://www.haskell.org}, Internet, 2019.

\bibitem{ocamlorg}
OCaml, hivatalos weboldal, \texttt{http://ocaml.org}, Internet, 2019.

\bibitem{gnutime}
GNU Time, hivatalos weboldal, \texttt{https://www.gnu.org/software/time}, \\
Internet, 2019.

\bibitem{coarsetime}
coarsetime, dokumentáció, \texttt{https://docs.rs/coarsetime/0.1.11/coarsetime}, Internet, 2019.

\bibitem{cppreference}
CPP Reference, \texttt{https://cppreference.com}, Internet, 2019.

\bibitem{gcc}
\texttt{https://gcc.gnu.org/}, Internet, 2019. március.

\bibitem{llvm}
Lattner, Chris. \emph{LLVM and Clang: Next generation compiler technology}. \\
The BSD conference. Vol. 5. 2008.

\bibitem{numericalrecipes}
William H. Press, Saul A. Teukolsky, William T. Vetterling, Brian P. Flannery: \emph{Numerical Recipes The Art of Scientific Computing Third Edition}. \\
Cambridge University Press, 2007.

\bibitem{ieee}
Hough, David. \emph{Applications of the proposed IEEE 754 standard for floating-point arithetic}. Computer 3 (1981): 70-74.

\bibitem{simpson}
Clenshaw, Charles W., and Alan R. Curtis. \emph{A method for numerical integration on an automatic computer}. Numerische Mathematik 2.1 (1960): 197-205.

\bibitem{heapsort}
Schaffer, Russel, and Robert Sedgewick. \emph{The analysis of heapsort}. Journal of Algorithms 15.1 (1993): 76-100.

\bibitem{shellsort}
Astrachan, Owen. \emph{Bubble sort: an archaeological algorithmic analysis}. ACM SIGCSE Bulletin. Vol. 35. No. 1. ACM, 2003.

\bibitem{sedgewickquicksort}
Robert Sedgewick: \emph{Implementing Quicksort programs}. Communications of the ACM 21.10 (Oct. 1978): 847-857.

\end{thebibliography}
